CLT item selection

### 2022-04-25 analysis/clt_item_selection.Rmd
More careful proposal function (cannot overwrite its own swaps).

proposal_fn <- function(subset) {
	swaps <- sample(c(1, 1, 1, 2, 2, 3), 1)
	for(i in 1:swaps) {
		active_items <- seq(1:length(subset))[subset == TRUE]
		inactive_items <- seq(1:length(subset))[subset == FALSE]
		active_to_swap <- sample(active_items, 1)
		inactive_to_swap <- sample(inactive_items, 1)
		subset[active_to_swap] <- FALSE
		subset[inactive_to_swap] <- TRUE
	}
	return(subset)
}

>>>>

proposal_fn <- function(subset) {
	# Randomly sample a number of swaps.
	# Prefer a small number of swaps for "fine tuning", but allow
	# occasional large numbers of swaps, including a complete
	# exchange of the subset
	subset_size = sum(as.integer(subset))
	max_swaps = min(subset_size, length(subset) - subset_size)
	swaps <- rbinom(1, max_swaps-1, 1/(max_swaps-1)) + 1

	# Choose the items to swap
	active_items <- seq(1:length(subset))[subset == TRUE]
	inactive_items <- seq(1:length(subset))[subset == FALSE]
	actives_to_swap <- sample(active_items, swaps)
	inactives_to_swap <- sample(inactive_items, swaps)

	# Do the swapping
	for(i in 1:swaps) {
		subset[actives_to_swap[i]] <- FALSE
		subset[inactives_to_swap[i]] <- TRUE
	}
	return(subset)
}
